### 2022-05-28 manuscript.Rmd

```{r, clusters, include=TRUE}
read_csv(clusters_file, col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> clusters

clusters %>%
  filter(p_val < .05) %>%
  ggplot(aes(x = time, y = channel, fill = cluster)) +
  facet_grid(~contrast, drop = FALSE) +
  geom_raster() +
  scale_fill_viridis_d()
```

>>>>

```{r, clusters, include=TRUE, fig.height=8}
# Read results of cluster-based permutation tests for ERPs
read_csv(clusters_file, col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> clusters

# Plot thresholded cluster images
clusters %>%
  filter(p_val < .05) %>%
  ggplot(aes(x = time, y = channel, fill = cluster)) +
  facet_grid(~contrast, drop = FALSE) +
  geom_raster() +
  theme(legend.position = "top")
```

```{r, tfr, include=TRUE, fig.height=12}
# Read results of cluster-based permutation tests for TFR
read_csv(tfr_clusters_file, col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> tfr_clusters

# Plot thresholded cluster images for the insight phase
tfr_clusters %>%
  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")

# Plot thresholded cluster images for the post-insight phase
tfr_clusters %>%
  filter(
    contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < .05
  ) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")
```
